Think deep for reef resilience

### 2025-08-09 paper/paper_draft.qmd
auto-format

The spatial extent of the GBR reefs represented in this investigation follows the reef
definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA)
[@GBRMPA2022]. An indicative map of the GBR marine park including the Marine Park
management regions and which reefal bioregion each reef belongs to is shown in
@fig-region-map [@GBRMPA2024; @GBRMPA2001]. This investigation adopts the GBR reef definition
used in Bozec et al. [-@bozec2025], which includes 3806 reefs across the GBR. Reefs that are not
associated with GBRMPA management areas or reefal bioregions were removed from the
investigation. Additionally, reefs with poor quality bathymetry data coverage or fewer than
three reefs per bioregion were removed from analyses (see Methods - Depth estimation). As a
result, a total of 2429 individual reefs were included in this investigation. Annually and
spatially averaged Degree Heating Week (DHW) data were used to represent future thermal
stress at each reef location. Code used to calculate DHW data and perform analyses involved
in this investigation can be found at **insert repo citation**.

@@

::: {#tbl-gcms}
| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
|-----------------------|-----------------------|-------------------------|-----------------------|
| EC-Earth3-Veg | 4.31 | High | **insert repo citation** |
| ACCESS-CM2 | 4.72 | High | **insert repo citation** |
| ACCESS-ESM1-5 | 3.87 | Intermediate | Main text |
| GFDL-CM4 | 2.9 | Low | **insert repo citation** |
| NorESM2-MM | 2.5 | Low | **insert repo citation** |

>>>>

The spatial extent of the GBR reefs represented in this investigation follows the reef
definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA)
[@GBRMPA2022]. An indicative map of the GBR marine park including the Marine Park management
regions and which reefal bioregion each reef belongs to is shown in [@fig-region-map;
@GBRMPA2024; @GBRMPA2001]. This investigation adopts the GBR reef definition used in Bozec
et al. [-@bozec2025], which includes 3806 reefs across the GBR. Reefs that are not
associated with GBRMPA management areas or reefal bioregions were removed from the
investigation. Additionally, reefs with poor quality bathymetry data coverage or fewer than
three reefs per bioregion were removed from analyses (see Methods - Depth estimation). As a
result, a total of 2429 individual reefs were included in this investigation. Annually and
spatially averaged Degree Heating Week (DHW) data were used to represent future thermal
stress at each reef location. Code used to calculate DHW data and perform analyses involved
in this investigation can be found at **insert repo citation**.

@@

::: {#tbl-gcms}
| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
|-----------------------|-----------------------|------------------------|-----------------------|
| EC-Earth3-Veg | 4.31 | High | **insert repo citation** |
| ACCESS-CM2 | 4.72 | High | **insert repo citation** |
| ACCESS-ESM1-5 | 3.87 | Intermediate | Main text |
| GFDL-CM4 | 2.9 | Low | **insert repo citation** |
| NorESM2-MM | 2.5 | Low | **insert repo citation** |
